The core transcriptome of mammalian placentas and the divergence of expression with placental shape

### 2016-11-17 manuscript/manuscript.Rnw
add FPKM 1 text to the figure

print(ggplot(cpt.distribution.shape[`Expression (FPKM)` > 0.1,],
             aes(x=`Expression (FPKM)`,color=`Min. Exp. in`,y=num_genes))
      + geom_line(lwd=1)
      + xlab("Minimum Expression cutoff (FPKM)")
      + ylab("Number of Genes Meeting FPKM Cutoff in N species")
      + scale_y_log10(breaks = trans_breaks("log10", function(x) 10^x),
                      labels = trans_format("log10", math_format(10^.x)))
      + scale_x_log10(breaks = trans_breaks("log10", function(x) 10^x),
                      labels = trans_format("log10", math_format(10^.x)))
      + geom_vline(xintercept=10,linetype="dotted")
      + geom_segment(mapping=aes(y=V1,
                         yend=V1,
                         xend=10,
                         x=300,
                         color=`Min. Exp. in`),
                     data=cpt.distribution.shape[`Expression (FPKM)` > 10,
                                              max(num_genes),`Min. Exp. in`],
                     arrow=arrow(length=unit(0.5,"cm")),
                     show.legend=FALSE
                     )
      + geom_text(mapping=aes(x=300,
                      y=V1,
                      label=paste0(V1," genes"),override=TRUE),
                  data=cpt.distribution.shape[`Expression (FPKM)` > 10,
                      max(num_genes),`Min. Exp. in`],
                  show.legend=FALSE,
                  hjust=0
                  )
      + guides(color=guide_legend(title=paste0("Min. Expression in\nn of ",num.species," Species"),
                                  keywidth=unit(3,"mm"),
                                  keyheight=unit(3,"mm"),
                                  title.hjust=0.5,
                                  label.position="right"
                                  ))
      + theme_bw()
      + theme(legend.position=c(0.98,0.98),
              legend.margin=unit(0,"mm"),
              legend.justification=c(1,1),
              plot.margin=unit(c(0,0,0,0),"mm")
              )
      )
@ 
\caption{Distribution shape of placenta core genes. The vertical axis
  shows the number of 1:1 orthologous genes included in the core
  placenta transcriptome if %
  \Sexpr{cpt.distribution.shape[,levels(`Min. Exp. in`)[1]]}
  %
  (or %
  \Sexpr{cpt.distribution.shape[,levels(`Min. Exp. in`)[2]]},
  % 
  etc.) have a minimum expression in FPKM equal to the horizontal axis.
  For example, if the cutoff is set to 10 (vertical black line), 
  % 
  \Sexpr{cpt.distribution.shape[`Expression (FPKM)` > 10 
    & `Min. Exp. in` == '14 of 14',max(num_genes)]}
  %
  genes would be included if the FPKM of a set of 1:1 orthologs of all 14 species must be at
  least 10, %
  \Sexpr{cpt.distribution.shape[`Expression (FPKM)` > 10 
    & `Min. Exp. in` == '13 of 14',max(num_genes)]}
  %
  1:1 orthologs would be included if 13 of 14 species have an
   with an FPKM of at least 10, and 
  \Sexpr{cpt.distribution.shape[`Expression (FPKM)` > 10 
    & `Min. Exp. in` == '10 of 14',max(num_genes)]}
  genes would be included if 10 of 14 species
  must have an FPKM of at least 10.}
\label{fig:core_placenta_transcriptome_shape}
\end{figure}

>>>>

print(ggplot(cpt.distribution.shape[`Expression (FPKM)` > 0.1,],
             aes(x=`Expression (FPKM)`,color=`Min. Exp. in`,y=num_genes))
      + geom_line(lwd=1)
      + xlab("Minimum Expression cutoff (FPKM)")
      + ylab("Number of Genes Meeting FPKM Cutoff in N species")
      + scale_y_log10(breaks = trans_breaks("log10", function(x) 10^x),
                      labels = trans_format("log10", math_format(10^.x)))
      + scale_x_log10(breaks = trans_breaks("log10", function(x) 10^x),
                      labels = trans_format("log10", math_format(10^.x)))
      + geom_vline(xintercept=10,linetype="dotted")
      + geom_segment(mapping=aes(y=V1,
                         yend=V1,
                         xend=10,
                         x=300,
                         color=`Min. Exp. in`),
                     data=cpt.distribution.shape[`Expression (FPKM)` > 10,
                                              max(num_genes),`Min. Exp. in`],
                     arrow=arrow(length=unit(0.5,"cm")),
                     show.legend=FALSE
                     )
      + geom_text(mapping=aes(x=300,
                      y=V1,
                      label=paste0(V1," genes"),override=TRUE),
                  data=cpt.distribution.shape[`Expression (FPKM)` > 10,
                      max(num_genes),`Min. Exp. in`],
                  show.legend=FALSE,
                  hjust=0
                  )
      + geom_segment(mapping=aes(yend=V1,
                         y=100,
                         xend=1,
                         x=1,
                         color=`Min. Exp. in`),
                     data=cpt.distribution.shape[`Expression (FPKM)` > 1 &
                                                 `Min. Exp. in` == '14 of 14',
                                                 max(num_genes),`Min. Exp. in`],
                     arrow=arrow(length=unit(0.5,"cm")),
                     show.legend=FALSE
                     )
      + geom_text(mapping=aes(x=1,
                      y=100,
                      label=paste0(V1," genes"),
                      override=TRUE),
                  angle=90,
                  data=cpt.distribution.shape[`Expression (FPKM)` > 1 &
                                              `Min. Exp. in` == '14 of 14',
                                              max(num_genes),`Min. Exp. in`],
                  show.legend=FALSE,
                  hjust=1
                  )
      + guides(color=guide_legend(title=paste0("Min. Expression in\nn of ",num.species," Species"),
                                  keywidth=unit(3,"mm"),
                                  keyheight=unit(3,"mm"),
                                  title.hjust=0.5,
                                  label.position="right"
                                  ))
      + theme_bw()
      + theme(legend.position=c(0.98,0.98),
              legend.margin=unit(0,"mm"),
              legend.justification=c(1,1),
              plot.margin=unit(c(0,0,0,0),"mm")
              )
      )
\caption{Distribution shape of placenta core genes. The vertical axis
  shows the number of 1:1 orthologous genes included in the core
  placenta transcriptome if %
  \Sexpr{cpt.distribution.shape[,levels(`Min. Exp. in`)[1]]}
  %
  (or %
  \Sexpr{cpt.distribution.shape[,levels(`Min. Exp. in`)[2]]},
  % 
  etc.) have a minimum expression in FPKM equal to the horizontal axis.
  For example, if the cutoff is set to 10 (vertical black line), 
  % 
  \Sexpr{cpt.distribution.shape[`Expression (FPKM)` > 10 
    & `Min. Exp. in` == '14 of 14',max(num_genes)]}
  %
  genes would be included if the FPKM of a set of 1:1 orthologs of all 14 species must be at
  least 10, %
  \Sexpr{cpt.distribution.shape[`Expression (FPKM)` > 10 
    & `Min. Exp. in` == '13 of 14',max(num_genes)]}
  %
  1:1 orthologs would be included if 13 of 14 species have an
   with an FPKM of at least 10, and 
  \Sexpr{cpt.distribution.shape[`Expression (FPKM)` > 10 
    & `Min. Exp. in` == '10 of 14',max(num_genes)]}
  genes would be included if 10 of 14 species
  must have an FPKM of at least 10.}
\label{fig:core_placenta_transcriptome_shape}
\end{figure}
